Optimal (Multiway) Spatial Joins

### 2024-05-26 msj.tex
yufei

@@

Performing the above for all $i, j \in [k]$ with $i \ne j$ results in a total time complexity of $O(k^3) \cdot (F_{k-1}(n, \out) + n \log n + k \cdot \out)$. A category-1 result tuple $\bm{t}$ may be seen more than once (this happens if the top-left corner of $B_\bm{t}$ is the top-left corner of more than one rectangle in $\bm{t}$). Duplicate removal can be achieved at no extra cost asymptotically, following the ideas explained in Section~\ref{sec:hv:type2}.

>>>>

\subsection{Proof of Theorem~\ref{thm:main-recur}} \label{sec:ksj:thm1}

@@

Performing the above for all $i, j \in [k]$ with $i \ne j$ results in a total time complexity of $O(k^3) \cdot (F_{k-1}(n, \out) + n \log n + k \cdot \out)$. A category-2 result tuple $\bm{t}$ may be seen more than once (this can happen if, for example, more than one rectangle in $\bm{t}$ has the same top-edge or the same left-edge). Again, duplicate removal can be achieved at no extra cost asymptotically.

We now complete the proof of Theorem~\ref{thm:main-recur}.
